Rapid cycleway prioritisation tool

### 2020-06-09 report.Rmd
Update report intro

The statutory guidance on network management in response to COVID-19 outlines a range of measures that can support a safe and healthy restart, including the creation of new cycleways, reducing speed limits, widening of footways and closing roads to motor traffic via 'modal filters'.
**This report describes the rapid cycleway prioritisation tool project, which provides aims to ensure evidence-based and effective investment in first of these measures: the creation of new cycleways in existing carriageway space reclaimed from motor traffic.**
Light segregation infrastructure such as flexible plastic wands (illustrated in Figure 1) and bollards can deliver a step change in provision for cycling, when implemented in combination with other measures such reduced speed limits on key corridors (as has happened on the A33 in Southampton and the A56 in Manchester) and when placed where they are most needed.
**The purpose of the tool is to help identify such key corridors, ensuring that funds from the Emergency Active Travel Fund change the status quo of urban and rural transport systems in favour of active travel.**

@@

<!-- https://twitter.com/doddyuk/status/1267146449227255808 -->

The £250m released by the Emergency Active Travel Fund will be spent in three broad [ways](https://www.transportxtra.com/publications/local-transport-today/news/65661/dft-releases-first-45m-of-250m-fund/):

- The first tranche: £45m released on 1^st^ June, is for swift interventions that must be implemented by the end of June
- The second tranche: £180m will be released later in the summer for more permanent measures
- £25m will be invested in cycle repair schemes

The emphasis of the evidence presented in this report is providing a strong evidence base to prioritisation of schemes eligible for the second tranche.
However, the evidence could also be used to support identification of schemes for the first tranche, such as reallocation of road space on arterial routes, where decisions have not yet been made.

Given the importance of acting quickly, and the unique opportunity that the crisis poses to improve physical activity levels in the long term, it is vital that local authorities have the evidence they need.
Without a nationally consistent and systematic evidence base, there is a risk that some already stretched local authorities will rely on ad-hoc methods to allocate funding.
The rapid cycleway prioritisation tool can also support authorities to make bold plans by highlighting the potential of key strategic corridors.

>>>>

The statutory guidance on network management in response to COVID-19 outlines a range of measures that can support a safe and healthy restart, including the creation of new cycleways, reducing speed limits, widening of footways and closing roads to motor traffic via 'modal filters'.
**This report describes the rapid cycleway prioritisation tool project, which provides aims help authorities effectively prioritise locations of new cycleways created by reallocating road space.**
<!-- Light segregation infrastructure such as flexible plastic wands (illustrated in Figure 1) and bollards can deliver a step change in provision for cycling, when implemented in combination with other measures such reduced speed limits on key corridors (as has happened on the A33 in Southampton and the A56 in Manchester) and when placed where they are most needed. -->

@@

<!-- https://twitter.com/doddyuk/status/1267146449227255808 -->
<!-- The purpose of the tool is to help identify such key corridors, ensuring that funds from the Emergency Active Travel Fund change the status quo of urban and rural transport systems in favour of active travel. -->

The Emergency Active Travel Fund allocated £225m for new infrastructure in two [tranches](https://www.transportxtra.com/publications/local-transport-today/news/65661/dft-releases-first-45m-of-250m-fund/):

- The first tranche: £45m allocated for swift interventions for which applications were submitted by authorities on 5^th^ June.
- The second tranche: £180m will be released later in the summer for permanent measures

The Rapid Cycleway Prioritisation Tool was designed to provide evidence in support of schemes eligible for the second tranche of funding.
Given the importance of acting quickly, and the unique opportunity that the crisis poses to improve physical activity levels in the long term, it is vital that local authorities have the evidence they need.
Without a nationally consistent and systematic evidence base, there is a risk that some already stretched local authorities will rely on ad-hoc methods to allocate funding.
The rapid cycleway prioritisation tool can also support authorities to make bold plans by highlighting the potential of key strategic corridors.
